{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or, How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-08-08 thesis/tm.tex
more tm reruns (same rerun pass as last commit, don't worry not crying yet)

\begin{table*}[t]
	\begin{center}
		\footnotesize
	\begin{tabular}{cc||r|r|r||r|r|r|r}
			&	&\multicolumn{3}{c||}{\bf Quicksand mode}&\multicolumn{4}{c}{{\bf Maximal state space mode} ({\tt -M})} \\
		\bf buggy test	& \bf params&\cpu{\bf cpu (s)}&\wtm{\bf wall (s)}&\ints{\bf int's}&\cpu{\bf cpu (s)}&\wtm{\bf wall (s)}&\ints{\bf int's}& \ETA{\bf SS size (est.)} \\
		\hline
		\hline
		{\tt htm1}
			& 2,1	&\cpu{  26.48}&\wtm{6.48}&\ints{5}& \cpu{*8.21}& \wtm{*5.78}& \ints{5	}& \ETA{12} \\
		(assertion)
			& 2,2	&\cpu{  45.23}&\wtm{8.28}&\ints{9}& \cpu{*8.42}& \wtm{*5.97}& \ints{9	}& \ETA{102} \\
			& 2,3	&\cpu{ 53.88}&\wtm{9.92}&\ints{17}& \cpu{*8.80}& \wtm{*6.31}& \ints{17	}& \ETA{819} \\
			& 2,4	&\cpu{ 90.24}&\wtm{14.63}&\ints{33}& \cpu{*9.72}& \wtm{*7.19}& \ints{33	}& \ETA{6553} \\
		\cline{2-9}
			& 3,1	&\cpu{ 39.75}&\wtm{8.21}&\ints{5}& \cpu{*8.15}& \wtm{*5.71}& \ints{5	}& \ETA{76} \\
			& 3,2	&\cpu{ 46.91}&\wtm{8.40}&\ints{9}& \cpu{*8.37}& \wtm{*5.91}& \ints{9	}& \ETA{3686} \\
			& 3,3	&\cpu{ 41.39}&\wtm{8.50}&\ints{17}& \cpu{*8.71}& \wtm{*6.26}& \ints{17	}& \ETA{176947} \\
			& 3,4	&\cpu{ 92.98}&\wtm{15.19}&\ints{33}& \cpu{*10.36}& \wtm{*7.15}& \ints{33	}& \ETA{8493465} \\
		\cline{2-9}
			& 4,1	&\cpu{ 45.13}&\wtm{8.56}&\ints{5}& \cpu{*7.77}& \wtm{*5.30}& \ints{5	}& \ETA{460} \\
			& 4,2	&\cpu{64.99}&\wtm{11.33}&\ints{9}& \cpu{*8.32}& \wtm{*5.59}& \ints{9	}& \ETA{132710} \\
		\hline
		{\tt swapbug}
			& 2,1	&\cpu{104.37}&\wtm{17.00}&\ints{*6}& \cpu{*43.76}& \wtm{*12.51}& \ints{33	}& \ETA{73} \\
		(deadlock)
			& 2,2	&\cpu{ 66.47}&\wtm{*12.42}&\ints{*38}& \cpu{*45.22}& \wtm{15.30}& \ints{85	}& \ETA{860} \\
			& 2,3	&\cpu{ 99.41}&\wtm{*15.92}&\ints{*48}& \cpu{*53.57}& \wtm{21.34}& \ints{217	}& \ETA{9120} \\
			& 2,4	&\cpu{125.23}&\wtm{*19.46}&\ints{*68}& \cpu{*71.01}& \wtm{38.86}& \ints{537	}& \ETA{91239} \\
		\cline{2-9}
			& 3,1	&\cpu{313.36}&\wtm{*44.50}&\ints{*34}&\cpu{*78.23}& \wtm{60.49}& \ints{1016	}& \ETA{3543} \\
			& 3,2	&\cpu{*6500.36}&\wtm{*816.27}&\ints{*262}&\ETA{--}&\ETA{>1h}&\ETA{--}& \ETA{2161715} \\
		\hline
		{\tt avl\_insert}
			& 2,2	&\cpu{1355.05}&\wtm{174.09}&\ints{*29}	&\cpu{*93.28}&\wtm{*30.37}&\ints{79}&\ETA{157286} \\
		(segfault+)
			& 2,3	&\cpu{402.91}&\wtm{*54.60}&\ints{*33}&\cpu{*228.16}&\wtm{125.89}&\ints{835}&\ETA{13664151} \\
			% TODO: these 2,3 ones alone are new + ok
			% 33 interleavings; 1 preemptions; job time 12s; pldi time 179368977; new-fixed pldi cputime 1403360474
			% 835 interleavings; 1 preemptions; job time 1m 42s; pldi time 135292827; new-fixed pldi cputime 235664920
			& 2,4	&\ETA{--}&\ETA{>1h}&\ETA{--}&\ETA{--}&\ETA{>1h}&\ETA{--}& \ETA{79020639} \\
			% this quicksand jerk required ulimit -n higher than 1024
			%
			% the jerk didn't even find the bug anymore, after dpor-preferred tid
			% heres the stats from how it did before
			% & 2,4	&\cpu{*7598.19}&\wtm{*970.67}&\ints{*2633}&\ETA{--}&\ETA{>1h}&\ETA{--}& \ETA{79020639} \\
			% anyway this was the maximal
			%
		\cline{2-9}
			& 3,1	&\cpu{*86.43}&\wtm{*14.10}&\ints{*23}	&\cpu{91.97}&\wtm{24.80}&\ints{53}&\ETA{343250} \\
			& 3,2	&\cpu{*2177.86}&\wtm{*287.66}&\ints{*169}&\ETA{--}&\ETA{>1h}&\ETA{--}& \ETA{425939133} \\
			% TODO
			%\multicolumn{9}{c}{everything above this line needs rerun for dpor-preferred tid + thr_bottom1} \\

@@

			& 3,2 & \cpu{2492.17}	& \ints{60606}	& \cpu{2040.98}	& \ints{44862}	& \cpu{565.97}	& \ints{14304} \\
			& 4,1 & \cpu{121.96}	& \ints{3006}	& \cpu{61.85}	& \ints{1296}	& \cpu{39.23}	& \ints{848} \\

@@

			& 2,1 & \cpu{38.76}	& \ints{99}	& \cpu{36.91}	& \ints{59}	& \cpu{3.29}	& \ints{4} \\
			& 2,2 & \cpu{12009.77}	& \ints{233396}	& \cpu{497.11}	& \ints{11427}	& \cpu{461.54}	& \ints{9046} \\
			& 3,1 & \cpu{2975.30}	& \ints{60912}	& \cpu{522.07}	& \ints{10706}	& \cpu{86.21}	& \ints{1014} \\
			%& 2,1 & \cpu{38.43}	& \ints{99}	& \cpu{36.12}	& \ints{59}	& \cpu{3.34}	& \ints{4} \\
			%& 3,1 & \cpu{vvv}	& \ints{vvv}	& \cpu{730.94}	& \ints{17112}	& \cpu{74.53}	& \ints{1064} \\

@@

@@

\begin{table}[t]
	\begin{center}
		\footnotesize
		\begin{tabular}{cc}
		\begin{tabular}{cc||r|r}
			& & \multicolumn{2}{c}{\bf STM ({\tt -A -S})} \\
			& & \cpu{\bf cpu (s)} & \ints{\bf SS size} \\
			\bf test & \bf params & \em (or \ETAdag{\bf \em est.}) & \em (or \ETAdag{\bf \em est.}) \\
			\hline
			\hline
			{\tt lock}
			& 2,1 & \cpu{3.41} & \ints{4} \\
			({\tt spinlock})
			& 2,2 & \cpu{198.77} & \ints{1702} \\
			% if lock(spin_fixed) will time out on 2,3 and 3,2, this is guaranteed to aswell
			& 3,1 & \cpu{35.28} & \ints{246} \\
			\hline
			{\tt lock}
			& 2,1 & \cpu{3.55} & \ints{4} \\
			({\tt spin\_fixed})
			& 2,2 & \cpu{105.57} & \ints{998} \\
			& 2,3 & \ETAdag{qqq} & \ETAdag{qqq} \\
			& 3,1 & \cpu{28.27} & \ints{186} \\
			& 3,2 & \ETAdag{qqq} & \ETAdag{qqq} \\
			& 4,1 & \cpu{qqq} & \ints {qqq} \\ % was: 30408, 282084 pre mkrun
			\hline
			{\tt lock}
			& 2,1 & \cpu{3.44} & \ints{4}		\\
			({\tt mutex})
			& 2,2 & \cpu{16.83} & \ints{180}	\\
			& 2,3 & \cpu{405.21} & \ints{9372}	\\
			& 2,4 & \cpu{qqq} & \ints{qqq}	\\ % was: 15266 sec 384512 pre mkrun
			& 3,1 & \cpu{15.00} & \ints{132}	\\
			%& 3,2 & \cpu{29432.87} & \ints{707086}	\\ % pre mkrun fix (let alone bottom1)
			& 3,2 & \ETAdag{qqq} & \ETAdag{qqq} \\
			& 4,1 & \cpu{665.89} & \ints{15064}	\\
			\hline
			{\tt lock\_fast}
			& 2,1 & \cpu{3.25} & \ints{1}	\\
			({\tt spin\_fixed})
			& 9,9 & \cpu{4.61} & \ints{1}	\\
			\hline
			{\tt lock\_fast}
			& 2,1 & \cpu{3.19} & \ints{1}	\\
			({\tt mutex})
			& 9,9 & \cpu{4.62} & \ints{1}	\\
			\end{tabular}
			&
			\begin{tabular}{cc||r|r}
			& & \multicolumn{2}{c}{\bf Non-transactional} \\
			& & \cpu{\bf cpu (s)} & \ints{\bf SS size} \\
			\bf test & \bf params & \em (or \ETAdag{\bf \em ETA}) & \em (or \ETAdag{\bf \em est.}) \\
			\hline
			\hline
			{\tt avl\_mutex}
			& 2,1 & \cpu{3.48} & \ints{7} \\
			& 2,2 & \cpu{6.25} & \ints{85} \\
			& 2,3 & \cpu{24.69} & \ints{561} \\
			& 2,4 & \cpu{217.98} & \ints{4984} \\
			& 3,1 & \cpu{8.26} & \ints{129} \\
			& 3,2 & \cpu{1403.46} & \ints{30653} \\
			& 3,3 & \ETAdag{qqq} & \ETAdag{qqq} \\
			& 4,1 & \cpu{199.96} & \ints{4488} \\
			& 4,2 & \ETAdag{qqq} & \ETAdag{qqq} \\
			\cline{1-4}
			{\tt map\_mutex}
			& 2,1 & \cpu{39.81} & \ints{83} \\
			& 2,2 & \cpu{qqq} & \ints{qqq} \\ % 30k and rising, looks like mb 5 hr? or 10+hr. 50/50 odds
			& 2,3 & \ETAdag{qqq} & \ETAdag{qqq} \\
			& 3,1 & \cpu{qqq} & \ints{qqq} \\ % 200k and rising, same tbh
			& 3,2 & \ETAdag{qqq} & \ETAdag{qqq} \\
			& 4,1 & \ETAdag{qqq} & \ETAdag{qqq} \\
			\\
			\\
			\\
			\\
			\\
		\end{tabular}
		\\
		\\
		(a) Verifying HTM locks alone.
		&
		(b) Verifying the lock's client code.
		\end{tabular}
	\end{center}
	\caption{Continuation of Table~\ref{tab:tm-verifs},
		demonstrating abstraction reduction \cite{dbug-phdthesis}
		on the {\tt avl\_fixed} and {\tt map\_basic} tests
		by verifying HTM mutex implementations separately.
		Tested with STM semantics, as both lock implementations include a retry loop.}
	\label{tab:tm-verifs2}
\end{table}

>>>>

\begin{table*}[t]
	\begin{center}
		\footnotesize
	\begin{tabular}{cc||r|r|r||r|r|r|r}
			&	&\multicolumn{3}{c||}{\bf Quicksand mode}&\multicolumn{4}{c}{{\bf Maximal state space mode} ({\tt -M})} \\
		\bf buggy test	& \bf params&\cpu{\bf cpu (s)}&\wtm{\bf wall (s)}&\ints{\bf int's}&\cpu{\bf cpu (s)}&\wtm{\bf wall (s)}&\ints{\bf int's}& \ETA{\bf SS size (est.)} \\
		\hline
		\hline
		{\tt htm1}
			& 2,1	&\cpu{  26.48}&\wtm{6.48}&\ints{5}& \cpu{*8.21}& \wtm{*5.78}& \ints{5	}& \ETA{12} \\
		(assertion)
			& 2,2	&\cpu{  45.23}&\wtm{8.28}&\ints{9}& \cpu{*8.42}& \wtm{*5.97}& \ints{9	}& \ETA{102} \\
			& 2,3	&\cpu{ 53.88}&\wtm{9.92}&\ints{17}& \cpu{*8.80}& \wtm{*6.31}& \ints{17	}& \ETA{819} \\
			& 2,4	&\cpu{ 90.24}&\wtm{14.63}&\ints{33}& \cpu{*9.72}& \wtm{*7.19}& \ints{33	}& \ETA{6553} \\
		\cline{2-9}
			& 3,1	&\cpu{ 39.75}&\wtm{8.21}&\ints{5}& \cpu{*8.15}& \wtm{*5.71}& \ints{5	}& \ETA{76} \\
			& 3,2	&\cpu{ 46.91}&\wtm{8.40}&\ints{9}& \cpu{*8.37}& \wtm{*5.91}& \ints{9	}& \ETA{3686} \\
			& 3,3	&\cpu{ 41.39}&\wtm{8.50}&\ints{17}& \cpu{*8.71}& \wtm{*6.26}& \ints{17	}& \ETA{176947} \\
			& 3,4	&\cpu{ 92.98}&\wtm{15.19}&\ints{33}& \cpu{*10.36}& \wtm{*7.15}& \ints{33	}& \ETA{8493465} \\
		\cline{2-9}
			& 4,1	&\cpu{ 45.13}&\wtm{8.56}&\ints{5}& \cpu{*7.77}& \wtm{*5.30}& \ints{5	}& \ETA{460} \\
			& 4,2	&\cpu{64.99}&\wtm{11.33}&\ints{9}& \cpu{*8.32}& \wtm{*5.59}& \ints{9	}& \ETA{132710} \\
		\hline
		{\tt swapbug}
			& 2,1	&\cpu{104.37}&\wtm{17.00}&\ints{*6}& \cpu{*43.76}& \wtm{*12.51}& \ints{33	}& \ETA{73} \\
		(deadlock)
			& 2,2	&\cpu{ 66.47}&\wtm{*12.42}&\ints{*38}& \cpu{*45.22}& \wtm{15.30}& \ints{85	}& \ETA{860} \\
			& 2,3	&\cpu{ 99.41}&\wtm{*15.92}&\ints{*48}& \cpu{*53.57}& \wtm{21.34}& \ints{217	}& \ETA{9120} \\
			& 2,4	&\cpu{125.23}&\wtm{*19.46}&\ints{*68}& \cpu{*71.01}& \wtm{38.86}& \ints{537	}& \ETA{91239} \\
		\cline{2-9}
			& 3,1	&\cpu{313.36}&\wtm{*44.50}&\ints{*34}&\cpu{*78.23}& \wtm{60.49}& \ints{1016	}& \ETA{3543} \\
			& 3,2	&\cpu{*6500.36}&\wtm{*816.27}&\ints{*262}&\ETA{--}&\ETA{>1h}&\ETA{--}& \ETA{2161715} \\
		\hline
		{\tt avl\_insert}
			& 2,2	&\cpu{1355.05}&\wtm{174.09}&\ints{*29}	&\cpu{*93.28}&\wtm{*30.37}&\ints{79}&\ETA{157286} \\
		(segfault+)
			& 2,3	&\cpu{402.91}&\wtm{*54.60}&\ints{*33}&\cpu{*228.16}&\wtm{125.89}&\ints{835}&\ETA{13664151} \\
			% TODO: these 2,3 ones alone are new + ok
			% 33 interleavings; 1 preemptions; job time 12s; pldi time 179368977; new-fixed pldi cputime 1403360474
			% 835 interleavings; 1 preemptions; job time 1m 42s; pldi time 135292827; new-fixed pldi cputime 235664920
			& 2,4	&\ETA{--}&\ETA{>1h}&\ETA{--}&\ETA{--}&\ETA{>1h}&\ETA{--}& \ETA{79020639} \\
			% this quicksand jerk required ulimit -n higher than 1024
			%
			% the jerk didn't even find the bug anymore, after dpor-preferred tid
			% heres the stats from how it did before
			% & 2,4	&\cpu{*7598.19}&\wtm{*970.67}&\ints{*2633}&\ETA{--}&\ETA{>1h}&\ETA{--}& \ETA{79020639} \\
			% anyway this was the maximal
			%
		\cline{2-9}
			& 3,1	&\cpu{*86.43}&\wtm{*14.10}&\ints{*23}	&\cpu{91.97}&\wtm{24.80}&\ints{53}&\ETA{343250} \\
			& 3,2	&\cpu{*2177.86}&\wtm{*287.66}&\ints{*169}&\ETA{--}&\ETA{>1h}&\ETA{--}& \ETA{425939133} \\
			% TODO
			\multicolumn{9}{c}{everything above this line needs rerun for dpor-preferred tid + thr\_bottom1} \\

@@

			% stm ok, rts ok, baseline alone needs redo
			& 3,2 & \cpu{2492.17}	& \ints{60606}	& \cpu{2363.41}	& \ints{44862}	& \cpu{639.62}	& \ints{14304} \\
			\multicolumn{8}{c}{everything above this line needs rerun for dpor-preferred tid + thr\_bottom1} \\
			& 4,1 & \cpu{129.25}	& \ints{3006}	& \cpu{64.91}	& \ints{1296}	& \cpu{40.78}	& \ints{848} \\

@@

			& 2,1 & \cpu{65.72}	& \ints{99}	& \cpu{66.05}	& \ints{59}	& \cpu{3.40}	& \ints{4} \\
			& 2,2 & \cpu{18124.06}	& \ints{277824}	& \cpu{1030.23}	& \ints{19542}	& \cpu{703.82}	& \ints{11600} \\
			& 3,1 & \cpu{3820.64}	& \ints{60912}	& \cpu{608.48}	& \ints{10706}	& \cpu{89.69}	& \ints{1014} \\

@@

		{\em Thesis draft note: Some of these tests still need to be rerun on account of landslide implementation updates
		to ensure consistent cpu times with the next table,
		but I expect the state space sizes not to change substantially.}

@@

\begin{table}[t]
	\begin{center}
		\footnotesize
		\begin{tabular}{cc}
		\begin{tabular}{cc||r|r}
			& & \multicolumn{2}{c}{\bf STM ({\tt -A -S})} \\
			& & \cpu{\bf cpu (s)} & \ints{\bf SS size} \\
			\bf test & \bf params & \em (or \ETAdag{\bf \em est.}) & \em (or \ETAdag{\bf \em est.}) \\
			\hline
			\hline
			{\tt lock}
			& 2,1 & \cpu{3.41} & \ints{4} \\
			({\tt spinlock})
			& 2,2 & \cpu{198.77} & \ints{1702} \\
			% if lock(spin_fixed) will time out on 2,3 and 3,2, this is guaranteed to aswell
			& 3,1 & \cpu{35.28} & \ints{246} \\
			\hline
			{\tt lock}
			& 2,1 & \cpu{3.55} & \ints{4} \\
			({\tt spin\_fixed})
			& 2,2 & \cpu{105.57} & \ints{998} \\
			& 2,3 & \ETAdag{qqq} & \ETAdag{qqq} \\
			& 3,1 & \cpu{28.27} & \ints{186} \\
			& 3,2 & \ETAdag{qqq} & \ETAdag{qqq} \\
			& 4,1 & \cpu{qqq} & \ints {qqq} \\ % was: 30408, 282084 pre mkrun
			\hline
			{\tt lock}
			& 2,1 & \cpu{3.44} & \ints{4}		\\
			({\tt mutex})
			& 2,2 & \cpu{16.83} & \ints{180}	\\
			& 2,3 & \cpu{405.21} & \ints{9372}	\\
			& 2,4 & \cpu{qqq} & \ints{qqq}	\\ % was: 15266 sec 384512 pre mkrun
			& 3,1 & \cpu{15.00} & \ints{132}	\\
			%& 3,2 & \cpu{29432.87} & \ints{707086}	\\ % pre mkrun fix (let alone bottom1)
			& 3,2 & \ETAdag{qqq} & \ETAdag{qqq} \\
			& 4,1 & \cpu{665.89} & \ints{15064}	\\
			\hline
			{\tt lock\_fast}
			& 2,1 & \cpu{3.25} & \ints{1}	\\
			({\tt spin\_fixed})
			& 9,9 & \cpu{4.61} & \ints{1}	\\
			\hline
			{\tt lock\_fast}
			& 2,1 & \cpu{3.19} & \ints{1}	\\
			({\tt mutex})
			& 9,9 & \cpu{4.62} & \ints{1}	\\
			\end{tabular}
			&
			\begin{tabular}{cc||r|r}
			& & \multicolumn{2}{c}{\bf Non-transactional} \\
			& & \cpu{\bf cpu (s)} & \ints{\bf SS size} \\
			\bf test & \bf params & \em (or \ETAdag{\bf \em ETA}) & \em (or \ETAdag{\bf \em est.}) \\
			\hline
			\hline
			{\tt avl\_mutex}
			& 2,1 & \cpu{3.48} & \ints{7} \\
			& 2,2 & \cpu{6.25} & \ints{85} \\
			& 2,3 & \cpu{24.69} & \ints{561} \\
			& 2,4 & \cpu{217.98} & \ints{4984} \\
			& 3,1 & \cpu{8.26} & \ints{129} \\
			& 3,2 & \cpu{1403.46} & \ints{30653} \\
			& 3,3 & \ETAdag{qqq} & \ETAdag{qqq} \\
			& 4,1 & \cpu{199.96} & \ints{4488} \\
			& 4,2 & \ETAdag{qqq} & \ETAdag{qqq} \\
			\cline{1-4}
			{\tt map\_mutex}
			& 2,1 & \cpu{39.81} & \ints{83} \\
			& 2,2 & \ETAdag{26h 21m} & \ETAdag{1085126} \\
			% [JOB 9] progress: 496530/1085126 brs (45.757812%), ETA 16h 21m 0s (elapsed 9h 59m 38s)
			% total CPU time consumed: 10h 19s (36019507965 usecs) (core saturation: 12%)
			& 3,1 & \ETAdag{qqq} & \ETAdag{qqq} \\
			\\
			\\
			\\
			\\
			\\
		\end{tabular}
		\\
		\\
		(a) Verifying HTM locks alone.
		&
		(b) Verifying the lock's client code.
		\end{tabular}
	\end{center}
	\caption{Continuation of Table~\ref{tab:tm-verifs},
		demonstrating abstraction reduction \cite{dbug-phdthesis}
		on the {\tt avl\_fixed} and {\tt map\_basic} tests
		by verifying HTM mutex implementations separately.
		Tested with STM semantics, as both lock implementations include a retry loop.}
	\label{tab:tm-verifs2}
\end{table}
